Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2019-01-28 SupportingInformation.Rmd
figure fixed

The noise ($\epsilon_{i}$), initially drawn from a bivariate asymmetric copula family, was transformed into a normally distribution with mean zero and standard deviation $0.1$ (considered as weak non-linear regime) or $1$ (considered as strongly non-linear), for code see [`GetNoise`](https://github.com/sghosh89/BIVAN/blob/master/Cause4copula.R) function. For weak non-linear regime, we found similar tail dependence in noise copula and the resultant population copula from the stochastic Ricker model (Figs. \ref{fig_Cause4copula_C_kend_sRicker} - \ref{fig_Cause4copula_SJ_kend_sRicker}) as we obtained in linear AR(1) model (see \nameref{MT-Results_Q2} in the maintext). But for strongly non-linear regime the tail-dependence between noise and population copula was not significantly similar (see the summary in Fig. \ref{fig_Cause4copula_kend_sRicker_nsd_1}). We repeated the whole analysis with $r > 1$ (i.e. Ricker model's over-compensatory dynamical regime) and came up with same conclusion that strong non-linearility could disturb the tail-dependence information translated from noise to population copula.

\begin{figure}[!h]
\begin{center}
\includegraphics[width=13 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Clayton/common_legend_cause4copula_stat.pdf}\\
\vspace{-0.4 cm}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Clayton/Clayton_Spearman_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Clayton/Clayton_Kendall_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Clayton/Clayton_Pearson_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Clayton/Clayton_Corl_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Clayton/Clayton_Coru_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Clayton/Clayton_Corl-Coru_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Clayton/Clayton_Pl_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Clayton/Clayton_Pu_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Clayton/Clayton_Pl-Pu_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Clayton/Clayton_D2u_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Clayton/Clayton_D2l_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Clayton/Clayton_D2u-D2l_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Clayton/Clayton_scatter_CorlmCoru_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Clayton/Clayton_scatter_PlmPu_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Clayton/Clayton_scatter_D2umD2l_Kendall's Tau.pdf}
\caption[Stochastic Ricker model with weak non-linearity: comparing correlations and non-parametric statistic between noise-copula (\textbf{Clayton}) and population copula for different Kendall's correlation]{Stochastic Ricker model with weak non-linearity: results of comparison between 3 types of correlation (i.e. Spearman, Kendall, Pearson) and 6 non-parametric stats ($\cor_l$, $\cor_u$, $\Ps_l$, $\Ps_u$, $\Dsq_u$ and $\Dsq_l$) of environmental noise generated from lower tail dependent \textbf{Clayton} copula and of the affected populations for 9 equidistant Kendall's correlation ($\tau$) values in a range (0.1 to 0.9) (Initially $5000$ points are generated but we kept last $500$ points for both noise and population data for comparison). p-values from paired t-test if $> 0.05$ (above horizontal purple line) indicates exactly same estimate between noise and population copulae. Last row in the figure compared the linear regression line with the 1:1 green line and if noise and population tail-dependence stats came up with pearson correlation p-value $< 0.05$, then they are significantly similar. \label{fig_Cause4copula_C_kend_sRicker}}
\end{center}
\end{figure}

\begin{figure}[!h]
\begin{center}
\includegraphics[width=13 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Survival Clayton/common_legend_cause4copula_stat.pdf}\\
\vspace{-0.4 cm}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Survival Clayton/Survival Clayton_Spearman_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Survival Clayton/Survival Clayton_Kendall_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Survival Clayton/Survival Clayton_Pearson_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Survival Clayton/Survival Clayton_Corl_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Survival Clayton/Survival Clayton_Coru_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Survival Clayton/Survival Clayton_Corl-Coru_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Survival Clayton/Survival Clayton_Pl_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Survival Clayton/Survival Clayton_Pu_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Survival Clayton/Survival Clayton_Pl-Pu_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Survival Clayton/Survival Clayton_D2u_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Survival Clayton/Survival Clayton_D2l_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Survival Clayton/Survival Clayton_D2u-D2l_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Survival Clayton/Survival Clayton_scatter_CorlmCoru_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Survival Clayton/Survival Clayton_scatter_PlmPu_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Survival Clayton/Survival Clayton_scatter_D2umD2l_Kendall's Tau.pdf}
\caption[Stochastic Ricker model with weak non-linearity: comparing correlations and non-parametric statistic between noise-copula (\textbf{Survival Clayton}) and population copula for different Kendall's correlation]{Stochastic Ricker model with weak non-linearity: similar analysis as depicted in Fig. \ref{fig_Cause4copula_C_kend_sRicker} but for noise generated from upper tail dependent \textbf{Survival Clayton} copula. \label{fig_Cause4copula_SC_kend_sRicker}}
\end{center}
\end{figure}

\begin{figure}[!h]
\begin{center}
\includegraphics[width=13 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Gumbel/common_legend_cause4copula_stat.pdf}\\
\vspace{-0.4 cm}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Gumbel/Gumbel_Spearman_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Gumbel/Gumbel_Kendall_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Gumbel/Gumbel_Pearson_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Gumbel/Gumbel_Corl_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Gumbel/Gumbel_Coru_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Gumbel/Gumbel_Corl-Coru_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Gumbel/Gumbel_Pl_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Gumbel/Gumbel_Pu_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Gumbel/Gumbel_Pl-Pu_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Gumbel/Gumbel_D2u_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Gumbel/Gumbel_D2l_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Gumbel/Gumbel_D2u-D2l_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Gumbel/Gumbel_scatter_CorlmCoru_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Gumbel/Gumbel_scatter_PlmPu_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Gumbel/Gumbel_scatter_D2umD2l_Kendall's Tau.pdf}
\caption[Stochastic Ricker model with weak non-linearity: comparing correlations and non-parametric statistic between noise-copula (\textbf{Gumbel}) and population copula for different Kendall's correlation]{Stochastic Ricker model with weak non-linearity: similar analysis as depicted in Fig. \ref{fig_Cause4copula_C_kend_sRicker} but for noise generated from upper tail dependent \textbf{Gumbel} copula. \label{fig_Cause4copula_G_kend_sRicker}}
\end{center}
\end{figure}

>>>>

The noise ($\epsilon_{i}$), initially drawn from a bivariate asymmetric copula family, was transformed into a normally distribution with mean zero and standard deviation $0.1$ (considered as weak noise) or $1$ (considered as strong noise), for code see [`GetNoise`](https://github.com/sghosh89/BIVAN/blob/master/Cause4copula.R) function. For weak noise, we found similar tail dependence in noise copula and the resultant population copula from the stochastic Ricker model (Figs. \ref{fig_Cause4copula_C_kend_sRicker_nsd_0.1} - \ref{fig_Cause4copula_SJ_kend_sRicker_nsd_0.1}) as we obtained in linear AR(1) model (see \nameref{MT-Results_Q2} in the maintext). But for strong noise the tail-dependence between noise and population copula was not significantly similar (Figs. \ref{fig_Cause4copula_C_kend_sRicker_nsd_1} - \ref{fig_Cause4copula_SJ_kend_sRicker_nsd_1}). We repeated the whole analysis with $r > 1$ (i.e. Ricker model's over-compensatory dynamical regime) and came up with same conclusion that strong noise with non-linearility could disturb the tail-dependence information translated from noise to population copula.

<!--adding results for stochastic ricker with weak noise : nsd=0.1-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=13 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Clayton/common_legend_cause4copula_stat.pdf}\\
\vspace{-0.4 cm}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Clayton/Clayton_Spearman_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Clayton/Clayton_Kendall_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Clayton/Clayton_Pearson_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Clayton/Clayton_Corl_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Clayton/Clayton_Coru_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Clayton/Clayton_Corl-Coru_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Clayton/Clayton_Pl_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Clayton/Clayton_Pu_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Clayton/Clayton_Pl-Pu_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Clayton/Clayton_D2u_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Clayton/Clayton_D2l_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Clayton/Clayton_D2u-D2l_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Clayton/Clayton_scatter_CorlmCoru_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Clayton/Clayton_scatter_PlmPu_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Clayton/Clayton_scatter_D2umD2l_Kendall's Tau.pdf}
\caption[Stochastic Ricker model with weak noise: comparing correlations and non-parametric statistic between noise-copula (\textbf{Clayton}) and population copula for different Kendall's correlation]{Stochastic Ricker model with weak nonise: results of comparison between 3 types of correlation (i.e. Spearman, Kendall, Pearson) and 6 non-parametric stats ($\cor_l$, $\cor_u$, $\Ps_l$, $\Ps_u$, $\Dsq_u$ and $\Dsq_l$) of environmental noise generated from lower tail dependent \textbf{Clayton} copula (having normal marginal with standard deviation 0.1) and of the affected populations for 9 equidistant Kendall's correlation ($\tau$) values in a range (0.1 to 0.9) (Initially $5000$ points are generated but we kept last $500$ points for both noise and population data for comparison). p-values from paired t-test if $> 0.05$ (above horizontal purple line) indicates exactly same estimate between noise and population copulae. Last row in the figure compared the linear regression line with the 1:1 green line and if noise and population tail-dependence stats came up with pearson correlation p-value $< 0.05$, then they are significantly similar. \label{fig_Cause4copula_C_kend_sRicker_nsd_0.1}}
\end{center}
\end{figure}

\begin{figure}[!h]
\begin{center}
\includegraphics[width=13 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Survival Clayton/common_legend_cause4copula_stat.pdf}\\
\vspace{-0.4 cm}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Survival Clayton/Survival Clayton_Spearman_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Survival Clayton/Survival Clayton_Kendall_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Survival Clayton/Survival Clayton_Pearson_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Survival Clayton/Survival Clayton_Corl_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Survival Clayton/Survival Clayton_Coru_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Survival Clayton/Survival Clayton_Corl-Coru_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Survival Clayton/Survival Clayton_Pl_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Survival Clayton/Survival Clayton_Pu_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Survival Clayton/Survival Clayton_Pl-Pu_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Survival Clayton/Survival Clayton_D2u_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Survival Clayton/Survival Clayton_D2l_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Survival Clayton/Survival Clayton_D2u-D2l_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Survival Clayton/Survival Clayton_scatter_CorlmCoru_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Survival Clayton/Survival Clayton_scatter_PlmPu_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Survival Clayton/Survival Clayton_scatter_D2umD2l_Kendall's Tau.pdf}
\caption[Stochastic Ricker model with weak noise: comparing correlations and non-parametric statistic between noise-copula (\textbf{Survival Clayton}) and population copula for different Kendall's correlation]{Stochastic Ricker model with weak noise: similar analysis as depicted in Fig. \ref{fig_Cause4copula_C_kend_sRicker_nsd_0.1} but for noise generated from upper tail dependent \textbf{Survival Clayton} copula having normal marginal with standard deviation 0.1. \label{fig_Cause4copula_SC_kend_sRicker_nsd_0.1}}
\end{center}
\end{figure}

\begin{figure}[!h]
\begin{center}
\includegraphics[width=13 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Gumbel/common_legend_cause4copula_stat.pdf}\\
\vspace{-0.4 cm}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Gumbel/Gumbel_Spearman_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Gumbel/Gumbel_Kendall_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Gumbel/Gumbel_Pearson_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Gumbel/Gumbel_Corl_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Gumbel/Gumbel_Coru_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Gumbel/Gumbel_Corl-Coru_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Gumbel/Gumbel_Pl_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Gumbel/Gumbel_Pu_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Gumbel/Gumbel_Pl-Pu_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Gumbel/Gumbel_D2u_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Gumbel/Gumbel_D2l_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Gumbel/Gumbel_D2u-D2l_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Gumbel/Gumbel_scatter_CorlmCoru_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Gumbel/Gumbel_scatter_PlmPu_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Gumbel/Gumbel_scatter_D2umD2l_Kendall's Tau.pdf}
\caption[Stochastic Ricker model with weak noise: comparing correlations and non-parametric statistic between noise-copula (\textbf{Gumbel}) and population copula for different Kendall's correlation]{Stochastic Ricker model with weak noise: similar analysis as depicted in Fig. \ref{fig_Cause4copula_C_kend_sRicker_nsd_0.1} but for noise generated from upper tail dependent \textbf{Gumbel} copula having normal marginal with standard deviation 0.1. \label{fig_Cause4copula_G_kend_sRicker_nsd_0.1}}
\end{center}
\end{figure}

\begin{figure}[!h]
\begin{center}
\includegraphics[width=13 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Survival Gumbel/common_legend_cause4copula_stat.pdf}\\
\vspace{-0.4 cm}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Survival Gumbel/Survival Gumbel_Spearman_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Survival Gumbel/Survival Gumbel_Kendall_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Survival Gumbel/Survival Gumbel_Pearson_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Survival Gumbel/Survival Gumbel_Corl_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Survival Gumbel/Survival Gumbel_Coru_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Survival Gumbel/Survival Gumbel_Corl-Coru_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Survival Gumbel/Survival Gumbel_Pl_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Survival Gumbel/Survival Gumbel_Pu_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Survival Gumbel/Survival Gumbel_Pl-Pu_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Survival Gumbel/Survival Gumbel_D2u_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Survival Gumbel/Survival Gumbel_D2l_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Survival Gumbel/Survival Gumbel_D2u-D2l_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Survival Gumbel/Survival Gumbel_scatter_CorlmCoru_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Survival Gumbel/Survival Gumbel_scatter_PlmPu_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Survival Gumbel/Survival Gumbel_scatter_D2umD2l_Kendall's Tau.pdf}
\caption[Stochastic Ricker model with weak noise: comparing correlations and non-parametric statistic between noise-copula (\textbf{Survival Gumbel}) and population copula for different Kendall's correlation]{Stochastic Ricker model with weak noise: similar analysis as depicted in Fig. \ref{fig_Cause4copula_C_kend_sRicker_nsd_0.1} but for noise generated from lower tail dependent \textbf{Survival Gumbel} copula having normal marginal with standard deviation 0.1. \label{fig_Cause4copula_SG_kend_sRicker_nsd_0.1}}
\end{center}
\end{figure}
